---
title: "Examining the relationship between county demogrpahic factors and voting outcomes"
output:
  revealjs::revealjs_presentation:
    theme: night
    highlight: zenburn
    center: true
    transition: fade
    slide_level: 2
---
```{r, echo=FALSE, results=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(stringr) 
library(corrplot) 
library(psych) 
library(GGally) 
library("jpeg")
```


## Summary of our data

```{r}
myData <- read.csv("../data/votes.csv") 
str(myData) 
```


## Cleaning our data 
```{r, echo=FALSE, results=FALSE, message=FALSE}
maindata <- myData %>%
  select(-1, -2, -3, -13, -14, -15, -16, -17, -18, -19, -20, -21, -22, -23, -24, -25, -27, -29, -79, -80, -81, -82)


relevant_1 <- maindata %>%
  select(7, 8, 9, 11, 12, 13, 14, 38, 44, 45, 46, 47, 48, 49, 50, 58, 27, 28)


colnames(relevant_1) <-c("DemPercentRepPercent", "State", "County", "PopulationChange", "PercentAgeUnder5", "PercentAgeUnder18", "PercentAgeOver65", "MedianHouseIncome", "NumberFirms", "PercentBlackFirms", "PercentNAFirms", "PercentAsianFirms", "PercentHawaiianFirms", "PercentHispanicFirms", "PercentWomenFirms", "Density", "PercentHSGrad", "PercentCollegeGrad")
``` 

```{r}
str(relevant_1)
```


## Percent Over 65 
```{r, echo=FALSE, results=FALSE, message=FALSE}
ggpairs(relevant_1[c('DemPercentRepPercent', 'PercentAgeOver65')], lower = list(continuous = wrap("smooth", color = 'blue', alpha = 0.3, size=0.3)))

```

## Percent of Women Firms
```{r, echo=FALSE, results=FALSE, message=FALSE}
ggpairs(relevant_1[c('DemPercentRepPercent', 'PercentWomenFirms')], lower = list(continuous = wrap("smooth", color = 'blue', alpha = 0.3, size=0.3)))
```


## Percent of Median House Income
```{r, echo=FALSE, results=FALSE, message=FALSE}
ggpairs(relevant_1[c('DemPercentRepPercent', 'MedianHouseIncome')], lower = list(continuous = wrap("smooth", color = 'blue', alpha = 0.3, size=0.3)))
```


## Percent of College Graduate
```{r, echo=FALSE, results=FALSE, message=FALSE}
ggpairs(relevant_1[c('DemPercentRepPercent', 'PercentCollegeGrad')], lower = list(continuous = wrap("smooth", color = 'blue', alpha = 0.3, size=0.3)))
```


## Hypothesis Test 

Null Hypothesis = None of our independent variables contributes significantly to our model 

Alternative Hypothesis = At least one of our independent variables contributes significantly to our model


## We are going to run a multi-linear regression...
```{r, echo=FALSE, results=FALSE, message=FALSE}
MultiRegression = lm(DemPercentRepPercent ~ PopulationChange + PercentAgeUnder5 + PercentAgeUnder18 + PercentAgeOver65 + MedianHouseIncome + PercentBlackFirms + PercentNAFirms + PercentAsianFirms + PercentHispanicFirms + PercentWomenFirms + Density + PercentHSGrad + PercentCollegeGrad, data = relevant_1)

```

```{r}
summary(MultiRegression)
```


## This is our more condensed model 

```{r, echo=FALSE, results=FALSE, message=FALSE}
CondensedModel = lm(DemPercentRepPercent ~ PercentAgeUnder18 + PercentAgeOver65 + PercentBlackFirms + PercentNAFirms +  PercentHispanicFirms + PercentCollegeGrad, data = relevant_1)

```

```{r}
summary(CondensedModel)
```


##   Extra Findings 


```{r, echo=FALSE, results=FALSE, message=FALSE}
MyPredData <- read.csv("../data/votes.csv")
```


```{r, echo=FALSE, results=FALSE, message=FALSE}
MainPredData <- MyPredData %>%
  select(-1, -2, -3, -13, -14, -15, -16, -17, -18, -19, -20, -21, -22, -23, -24, -25, -27, -29, -79, -80, -81, -82)
MainPredData
```



```{r, echo=FALSE, results=FALSE, message=FALSE}
relevant_p <- MainPredData %>%
  select(7, 8, 9, 11, 12, 13, 14, 38, 44, 45, 46, 47, 48, 49, 50, 58, 27, 28)
relevant_p
```


```{r, echo=FALSE, results=FALSE, message=FALSE}
colnames(relevant_p) <-c("DemPercentRepPercent", "State", "County", "PopulationChange", "PercentAgeUnder5", "PercentAgeUnder18", "PercentAgeOver65", "MedianHouseIncome", "NumberFirms", "PercentBlackFirms", "PercentNAFirms", "PercentAsianFirms", "PercentHawaiianFirms", "PercentHispanicFirms", "PercentWomenFirms", "Density", "PercentHSGrad", "PercentCollegeGrad")

```


## Let's set the sizes of the training and validation data sets. 

```{r}
 trainSize <- round(nrow(relevant_p) * 0.7)
 testSize <- nrow(relevant_p) - trainSize
```

## Let's partition the data

```{r}
set.seed(1)
 training_indices <- sample(seq_len(nrow(relevant_p)),
   size=trainSize)
 trainSet <- relevant_p[training_indices, ]
 testSet <- relevant_p[-training_indices, ]
```



```{r, echo=FALSE, results=FALSE, message=FALSE}
model <- lm(DemPercentRepPercent ~ PopulationChange + PercentAgeUnder5 + PercentAgeUnder18 + PercentAgeOver65 + MedianHouseIncome + NumberFirms + PercentBlackFirms + PercentNAFirms + PercentAsianFirms + PercentHawaiianFirms + PercentHispanicFirms + PercentWomenFirms + Density + PercentHSGrad + PercentCollegeGrad, data=trainSet)

summary(model)
```


```{r, echo=FALSE, results=FALSE, message=FALSE}
model1 <- lm(DemPercentRepPercent ~ PopulationChange + PercentAgeUnder5 + PercentAgeUnder18 + PercentAgeOver65 + MedianHouseIncome + NumberFirms + PercentBlackFirms + PercentNAFirms + PercentAsianFirms + PercentHispanicFirms + PercentWomenFirms + Density + PercentHSGrad + PercentCollegeGrad, data=trainSet)

summary(model1)
```

## This looks like a good model.
```{r}
model2 <- lm(DemPercentRepPercent ~ PopulationChange + PercentAgeUnder5 + PercentAgeUnder18 + PercentAgeOver65 + MedianHouseIncome + PercentBlackFirms + PercentNAFirms + PercentAsianFirms + PercentHispanicFirms + PercentWomenFirms + Density + PercentHSGrad + PercentCollegeGrad, data=trainSet)

summary(model2)
```

## Let's make predictions

```{r}
predictions <- predict(model2, testSet) 
```


## Train RMSE 

```{r}
sqrt(mean((trainSet$DemPercentRepPercent - predict(model2, trainSet)) ^ 2))
```


## Test RMSE

```{r}
sqrt(mean((testSet$DemPercentRepPercent - predict(model2, testSet)) ^ 2))
```

## Model for a hypothetical county we would expect to vote more Democrat

```{r}

predict(model2, newdata = data.frame(
  PopulationChange = -8,
  PercentAgeUnder5 = 8,
  PercentAgeUnder18 = 15,
  PercentAgeOver65 = 10,
  MedianHouseIncome = 35000,
  PercentBlackFirms = 15,
  PercentNAFirms = 3,
  PercentAsianFirms = 10,
  PercentHispanicFirms = 15,
  PercentWomenFirms = 40,
  Density = 4000,
  PercentHSGrad = 80,
  PercentCollegeGrad = 35
  
  
))
```

## Model for a hypothetical county we would expect to vote more Republican

```{r}

predict(model2, newdata = data.frame(
  PopulationChange = 8,
  PercentAgeUnder5 = 2,
  PercentAgeUnder18 = 25,
  PercentAgeOver65 = 30,
  MedianHouseIncome = 100000,
  PercentBlackFirms = 0,
  PercentNAFirms = 0,
  PercentAsianFirms = 0,
  PercentHispanicFirms = 0,
  PercentWomenFirms = 0,
  Density = 1,
  PercentHSGrad = 50,
  PercentCollegeGrad = 15
  
  
))
```



